Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-24 VMCAI-revised-version/final.tex
effectivity

   \multirow{2}{*}{sRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} NON
   		 & WSTS (downward + upward) Thm~9 \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Reset-VASS, WSTS ($\pred$-basis-effective+...) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline

@@

On the positive side, let us recall a result about {\sc Bounded-state-resilience} (called resilience in \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}).
%
%		(\"Ozkan,   \"Ozkan and W{\"{u}}rdemann,  
%
\alain{je ne comprends pas pourquoi les citations ne sortent pas comme les autres}
\begin{theorem}\label{ref ozkan}[Theorem 1,~\cite{DBLP:conf/gg/Ozkan22}, Theorem 1, ~\cite{DBLP:journals/corr/abs-2108-00889}]
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
when
$\Safe=\mathop{\uparrow} \Safe$.
\end{theorem}

>>>>

   \multirow{2}{*}{sRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{post srp} NON
   		 & WSTS (downward + upward) Thm~9 \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & Reset-VASS, WSTS ($\pred$-basis-effective) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WSTS ($\pred$-basis-effective + $\post^*$-basis-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (downward + upward) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-basis-effective+$\post$-effective) Prop~\ref{srp up down} & ?    \\ \hline

@@

On the positive side, let us recall a result about {\sc Bounded-state-resilience} (called resilience in \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}).
%
%		(\"Ozkan,   \"Ozkan and W{\"{u}}rdemann,  
%
\alain{je ne comprends pas pourquoi les citations ne sortent pas comme les autres}
\begin{theorem}[Theorem 1,~\cite{DBLP:conf/gg/Ozkan22}, Theorem 1, ~\cite{DBLP:journals/corr/abs-2108-00889}]\label{ref ozkan}
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
when
$\Safe=\mathop{\uparrow} \Safe$.
\end{theorem}
